Universal Anonymous Signatures

### 2022-06-07 prism-backend/research/gsac/security-uas.tex
Updated sign-unforgeability proof.

    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
        \sig as $(\NIZKproof,\Ec)$} \\
      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
        \PUBIK[\siid]$} \\
      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
      \sipk,\opk)): \pcreturn \bot \\
      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
      \NIZKtrap, (\msg,\feval,\yeval,\Ec,\sipk,\opk),\NIZKproof) \\
      \pcreturn (\usk,\scred,\attrs_{\scred},\yinsp) \\
    }

@@

    \procedure{$\IdentifyUK(\uid,\usk)$}{%
      \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      \pcfor \cid~\st~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
      \pcind \pcif \usk = \usk': \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
\end{figure}

@@

\begin{theorem}[Anonymity of \CUASGen]
  \label{thm:anonymity-uas}
  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, our
  \CUASGen construction satisfies anonymity as defined in
  \defref{def:anonymity-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
  \figref{fig:anon-sim}.

  \begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
      \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
      (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
      \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
      (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
      \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
      (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
      \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
      \textrm{Compute}~\Cparm,\SBCMparm,\Sparm,\Eparm~\textrm{as in}~\Setup \\
      \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
      \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
      (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
    }

    \begin{minipage}[t]{\textwidth}
      \begin{minipage}[t]{0.5\textwidth}
        \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \sipk_{\scred} \gets \PUBIK[\scid] \\
          \langle \cred, \cdot \rangle \gets
          \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\      
        }
        \end{minipage}
        \begin{minipage}[t]{0.5\textwidth}
          \procedure{$SimObt(\attrs,\sipk_{\scred})$}{%
            \textrm{Runs \SBCM}
            \textrm{Runs like \Obtain, replacing calls to
            $\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
            (\Ccom,\attrs,\sipk_{\scred}),
            (\usk,\scred,\attrs_{\scred},r))$ with calls to
            $\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},
            (\Ccom,\attrs,\sipk_{\scred}))$}
        }
        \end{minipage}
      \end{minipage}
    \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
    }

    \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sim-anon}
  \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
    anonymity in \CUASGen.}
\end{figure}

  \iffalse
  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

  We start from $G_0=\ExpAnonb$, and define game $G_1$ to be exactly the same
  as $G_0$, except that, within the $\Setup$ algorithm, we replace
  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
  $G_1$ is indistinguishable from $G_0$.

  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
  (i.e., \ExpAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
  \Ec_{\yinsp},\PUBIK[\scid_0],\PUBOK[\oid]),(\PRVUK[\cuid_0],
  \CRED[\scid_0],\attrs_{\scid_0},\yinsp,r))$ and $\Ec_{\yinsp} =
  \EEnc(\PUBOK[\oid],\yinsp;r)$.
  %
  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
  is, in $G_{2,0}$, $\csig_0 = (\pi_0^s,\Ec_{\yinsp})$, where $\pi^s_0 =
  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \Ec_{\yinsp},\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.

  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
  for $b=1$, where the challenge
  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
  \Ec_{\yinsp})$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  (\msg,\feval,\yeval,\Ec_{\yinsp},\PUBIK[\scid_1],\PUBOK[\oid]),
  (\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yinsp,r'))$ and $\Ec_{\yinsp}
  = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from $G_1^1$,
  simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\Ec_{\yinsp})$,
  where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,
  \feval,\yeval,\Ec_{\yinsp},\PUBIK[\scid_1],\PUBOK[\oid]))$. Again, by
  zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is indistinguishable from $G_1^1$.
  Note also that $G_2^1=G_2^0$ as, in the challenge oracle used in the
  anonymity game, we restrict to $\PUBIK[\scid_0] = \PUBIK[\scid_1]$.

  Finally, consider the definition of $\AdvAnon=|\Pr\lbrack
  \ExpAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$. As
  argued, $G_1$ is indistinguishable from $\ExpAnonb$, thus
  $\AdvAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
  \AdvAnon is negligible.
  \fi
  %
  \qed
\end{proof}

@@

\begin{proof}[\thmref{thm:issue-forge-uas}; Issue unforgeability of \CUASGen]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is zero-knowledge, sound,
  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Open}$ is sound
  and simulation extractable, and \SBCM is one-more unforgeable, then our
  \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.

  From $G_1$, and in order to define the winning conditions for the adversary
  in the signing unforgeability game, consider the following events:

  \begin{description}
  \item[$V$.] Where $V = \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$.
  \item[$J$.] Where $J = \Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,
    \feval) = 0$.
  \item[$L$.] Where $L = (\msg,\feval,\yeval,\Ec,\sipk,\opk) \in
    \NIZKLang^{\Sign}$.    
  \item[$I$.] Where $I = \exists \cred \in \scred~\st~\IdentifyCred(\usk,
    \attrs_{\cred},\msg) = 0$.
  \end{description}

  $\adv$ wins if $V \land (J \lor I) = (\overline{L} \land V \land (J \lor I))
  \lor (L \land V \land (J \lor I))$.
  %
  $V$ implies that $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$.
  Thus, after soundness of $\NIZK^{\Sign}$, the probability of $\overline{L}
  \land V \land (J \lor I)$ is negligible in the security parameter.
  %
  For $(L \land V \land (J \lor I))$ to be satisfied, there are three cases:
  \begin{enumerate}
  \item $L \land V \land J \land \overline{I}$. The game returns 1 in step 6.
  \item $L \land V \land J \land I$.  The game returns 1 in step 6.
  \item $L \land V \land \overline{J} \land I$. The game returns 1 in step 10. 
  \end{enumerate}

  In case 1, $L \land V$ implies that $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in
  \NIZKRel^{\Sign}$. More concretely, soundness of $NIZK^{\Sign}$ implies that
  $\Ec = \EEnc(\opk,\yinsp;r)$, for $\yinsp$ and $r$ known to the signer. Since
  $(\yinsp,\iproof)$ is generated honestly by the challenger from
  $(\opk,\sipk,\sig = (\NIZKproof_{\Sign},\Ec),\yeval,\msg)$, correctness of
  public key encryption implies that $\EDec(\osk,\Ec) = \yinsp$. Consequently,
  the probability of $L \land V \land J \land \overline{I}$ = 0, as \Judge
  checks precisely that \Ec is a correct encryption of \yinsp under \opk.

  The analysis for case 2 is the same as for case 1.

  For case 3, $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$,
  $\Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,\feval)
  = 1$, but there exists some credential \cred for which $\IdentifyCred(\usk,
  \attrs_{\cred},\msg)=0$. Note that \usk, $\attrs_{\cred}$ and \cred (for all
  $\cred \in \scred$) are output by \ExtractSign. Thus, after the
  simulation-extractability property and soundness of $\NIZK^{\Sign}$, $(\msg,
  \feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely
  means that, for all $\cred \in \scred$, $\SBCMVerify(\ipk_{\cred},\cred,\usk,
  \attrs_{\cred}) = 1 = \IdentifyCred(\usk,\attrs_{\cred},\cred)$. The
  probability of case 3 is therefore $0$.
  %
  Moreover, since \SBCMVerify returns $1$ for all $\cred \in \scred$, it must
  be that all of them were obtained via queries to the \ISSUE or \OBTISS
  oracles. Otherwise, if there exists some \cred that was not obtained via
  a call to these oracles, the tuple $(\usk, \attrs_{\cred}, \cred)$ constitutes
  a forgery of \SBCM.

  Cases 1, 2 and 3 above account for winning conditions at steps 6 and 10.
  % 
  Additionally, $\adv$ wins at step 8 if $\feval(\usk,\scred,\msg) \neq \yeval$,
  where \yeval is the value output by the adversary in step 2. However, since
  $\Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$, soundness of $NIZK^{\Sign}$
  implies that this has negligible probability.
  %
  Similarly, $\adv$ wins at step 9 if (1) $\finsp(\yeval,\usk,\scred,\msg) \neq
  \yinsp$, where \yinsp is the value output by \Open at line 5; or if (2)
  $\yinsp \neq \yinsp'$, where $\yinsp'$ is the value extracted by \ExtractSign
  at step 7. For (1), soundness of $\NIZK^{\Sign}$ ensures that \yinsp is the
  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Open}$ and
  correctness of the public key encryption ensure that this is also the value
  output by \Open. Thus, the probability of $\adv$ winning the game because
  of (1) is negligible. Finally, for (2), simulation-extractability of
  $\NIZK^{\Open}$ and correctness of the public key encryption ensure that
  the $\yinsp'$ value extracted by \NIZKExtract matches the value produced by
  \Open.

  The only remaining option for $\adv$ to win is via winning condition at line
  11. At that point, we already know that all credentials are bound to the same
  user key (otherwise, the adversary wins at line 10). If this key is not
  associated to any known user, this means that there is no matching $\langle
  \Obtain,\Issue\rangle$ transcript for a credential over $\usk$ --i.e., the
  honest issuer did not issue any credential to \usk. But, as \sig must have
  been produced with at least one credential (extracted at step 7), then this
  credential is a forgery, breaking security against one-more forgery of the
  \SBCM scheme.  
  %
  \qed
\end{proof}

>>>>

    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
        \sig as $(\NIZKproof,\Ec)$} \\
      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
        \PUBIK[\siid]$} \\
      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
      \sipk,\opk)): \pcreturn \bot \\
      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
      \NIZKtrap, (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
      \NIZKproof) \\
      \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
    }

@@

    \procedure{$\IdentifyUK(\uid,\usk)$}{%
      \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
      \pcind \pcif \usk = \usk': \pcreturn 1 \\
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
\end{figure}

@@

\begin{theorem}[Signature anonymity of \CUASGen]
  \label{thm:sign-anonymity-uas}
  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]
  \iffalse
  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
  \figref{fig:anon-sim}.

  \begin{figure}[ht!]
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
        (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
        \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
        (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
        \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
        (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
        \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
        \textrm{Compute}~\parm \gets (\Cparm,\SBCMparm,\Sparm,\Eparm)~
        \textrm{as in}~\Setup \\
        \pcreturn ((\parm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
        (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
      }

      \begin{minipage}[t]{\textwidth}
        \begin{minipage}[t]{0.55\textwidth}
          \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
            \pcif \uid \notin \HU: \pcreturn \bot \\
            \pcif \iid \notin \CI: \pcreturn \bot \\
            \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
            \sipk_{\scred} \gets \PUBIK[\scid] \\
            \langle \cred, \cdot \rangle \gets
            \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
            \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
            \pcreturn \top \\      
          }
        \end{minipage}
        \begin{minipage}[t]{0.45\textwidth}
          \procedure{$SimObt(\attrs,\ipk,\sipk_{\scred})$}{%
            \textrm{Runs $\langle \SBCMCom^{\NIZKRel_{\Issue}},\adv \rangle$} \\
            \pcind \textrm{using $\NIZKSim^{\NIZKRel_{\Issue}}
              (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},\cdot)$} \\
            \pcind \textrm{instead of $\NIZKProve^{\NIZKRel_{\Issue}}
              (\NIZKcrs_{\Issue},\cdot,\cdot)$}
          }
        \end{minipage}
      \end{minipage}

      \begin{minipage}[t]{\textwidth}
        \begin{minipage}[t]{0.55\textwidth}
          \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
            \pcif \uid \notin \HU: \pcreturn \bot \\
            \pcif \feval \notin \famfeval: \pcreturn \bot \\
            \Sig \gets SimSign(\PUBOK[\oid],\msg,\feval) \\
            \SIG[\uid] \gets \SIG[\uid] \cup
            \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
            \pcreturn \Sig \\
          }
        \end{minipage}
        \begin{minipage}[t]{0.45\textwidth}
          \procedure{$SimSign(\opk,\msg,\feval)$}{%
            \textrm{Like}~\Sign()~\textrm{using} \\
            \pcind \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
            \NIZKtrap_{\Sign},\cdot) \\
            \pcind \textrm{instead of}~\NIZKProve^{\NIZKRel_{\Sign}}
            (\NIZKcrs_{\Sign},\cdot,\cdot)        
          }
        \end{minipage}
      \end{minipage}

      \begin{minipage}[t]{\textwidth}
        \begin{minipage}[t]{0.55\textwidth}
          \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
            \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
            \in \SIG[\uid] \\
            % \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
            (\yinsp,\iproof) \gets
            SimOpen(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
            \pcif \CSIG[\Sig] \neq \bot: \\
            \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
              \feval$} \\
            \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
            \pcind (\yinsp',\iproof') \gets
            \Open(\PRVOK[\oid],\IK[\siid],\\
            \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
            \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
            \pcreturn (\yinsp,\iproof)          
          }
        \end{minipage}
        \begin{minipage}[t]{0.45\textwidth}
          \procedure{$SimOpen(\opk,\msg,\feval)$}{%
          }
        \end{minipage}
      \end{minipage}    
    \end{minipage}
    \label{fig:sim-anon}
    \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
      anonymity in \CUASGen.}
  \end{figure}
  \fi

  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

  We start from $G_0=\ExpSigAnonb$, and define game $G_1$ to be exactly the same
  as $G_0$, except that, within the $\Setup$ algorithm, we replace
  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
  $G_1$ is indistinguishable from $G_0$.

  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
  (i.e., \ExpSigAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
  % 
  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
  is, in $G_2^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.

  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
  for $b=1$, where the challenge
  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from
  $G_1^1$, simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\ceval,
  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is
  indistinguishable from $G_1^1$. Note also that $G_2^1$ and $G_2^0$ are
  indistinguishable, due to the IND-CCA property of the encryption scheme
  (so, the \ceval values in $\pi^s_0$ and $\pi^s_1$ are indistinguishable),
  in the  challenge oracle used in the anonymity game, we restrict to
  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
  the same \yinsp value.

  Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$. As
  argued, $G_1$ is indistinguishable from $\ExpSigAnonb$, thus
  $\AdvSigAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
  \AdvSigAnon is negligible.
  % 
  \qed
\end{proof}

@@

\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.

@@

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}
  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
  then our \CUASGen construction satisfies signing unforgeability as defined in
  \defref{def:sign-forge-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
  %
  Next, we show that an adversary winning $G_1$ can be used to break the
  one-more unforgeability property of \SBCM.

  If the verification at line 4 holds, then $(\msg,\feval,\yeval,\ceval,
  \cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
  %

  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
  \EEnc(\Eek,\yinsp)$, and since the $(\yinsp,\iproof)$ is generated honestly at
  line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.

  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:

  \begin{itemize}
  \item $\yeval^0 = \yeval$, where $(\yeval^0,\cdot) = \feval(\usk,\scred,
    \msg)$, and $\yeval$ is as output by \adv~at step 2.    
  \item $\tyeval^1 = \yeval^1$, where $(\cdot,\yeval^1) = \feval(\usk,\scred,
    \msg)$, and $\tyeval^1$ is as extracted by \ExtractSign at line 7.
  \end{itemize}

  Thus, the probability of \adv~winning at line 9 is $0$.

  \paragraph{(c) The output of \finsp matches the output of \Open.} %
  After (a), the \yinsp value output by \Open is the correct decryption of
  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)
  = \yinsp$ and, also, that \yinsp matches the $\yinsp'$ value extracted by
  \ExtractSign. Thus, the probability of \adv~winning at line 10 is $0$.

  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
  $\NIZKRel^{\Sign}$ includes a condition that $\forall \cred \in \scred,
  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1$. Thus, simulation
  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
  credentials involved in the signature contain \usk as their user key (first)
  attribute. Consequently, \IdentifyCred returns $1$ for all the involved
  credentials, and the probability of \adv~winning at line 11 is $0$.

  \paragraph{(e) \usk must belong to a known user.} %
  The only remaining option for $\adv$ to win is via winning condition at line
  12, meaning that \IdentifyUK fails to find an honest or corrupt users with
  a \usk matching the one used to request the credentials used to produce the
  signature output by \adv. However, at line 12, we already know that all
  credentials are valid signatures by the issuer and that, also, all are bound
  to the same user key. If this key is not associated to any known user, this
  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
  a credential over \usk --i.e., the honest issuer did not issue any credential
  to \usk. But, as \sig must have been produced with at least one credential
  (extracted at step 7), then this credential is a forgery, breaking security
  against one-more forgery of the \SBCM scheme.
  %
  \qed
\end{proof}
